---
title: "first_package"
author: "Egor Smirnov"
format: html
---

# Shared Properties

## Libraries

```{r libraries}
library(devtools)
library(usethis)
```

## Checks

```{r check}
has_devel()
```

```{r version}
packageVersion("usethis")
```

```{r git}
git_sitrep()
```

```{r vaccinate_true}
#it sets vaccinated to true,
#git_vaccinate()
```

```{r configure_main}
#it sets default initial branch to main
#git_default_branch_configure()
```

```{r token_create}
#it automatically moves you to the page to create a token
#create_github_token()
```

```{r token_set}
#it allows you to paste your new token
#gitcreds::gitcreds_set()
```

## Create Package

```{r}
create_package("~/Desktop/animalsounds")
```

## Git

```{r}
use_git()
```

```{r}
use_github()
```

```{r}
use_r("animal_sounds")
```

# First day

`Shift+Cmd+L`: activates `devtools::load_all(".")`. It allows to run packages as if it's in memory.

## Install

```{r install}
devtools::install()
```


## Licenses

open source: mit

gpl license: anything else that uses gpl should also use gpl

# Second day

```{r}
packageVersion("roxygen2")
```

`#'` is a roxygen comment.

`@param arg` is a roxygen tag (takes an argument, describes inputs). Common tags: `@examples` (shows how the function works), `@return` (describes the return value), `@export` (if the function should be user-visible).

Comments should start with a description block: Title (up to 65 characters), Description (few lines), Details.

RStudio allows to put automatically the roxygen comment: option+shift+cmd+R

You must have loaded the package with `load_all()` at least once.

Redular workflow: 1) update R comment, 2) update `.Rd` files, 3) preview `.html`, 4) continue.

A namespace splits functions into two classes: internal, external (must be documented, changing could break other people's code).
